\LARGE{\bf{Natural variation in teosinte at the domestication locus \emph{teosinte branched1} (\emph{tb1})}}\footnotemark

### 2014-09-10 manuscript.tex
minor

Domesticated crops and their wild progenitors provide an excellent system in which to study adaptation and genomic changes associated with human-mediated selection \citep{Ross-Ibarra2007}. 
Plant domestication usually involves a suite of phenotypic changes such as loss of seed shattering and increased fruit or grain size, which are commonly referred to as `domestication syndrome' \citep{OlsenWendel2013}, and much of the study of domestication has focused on understanding the genetic variation underlying these traits \citep{OlsenGross2010}. 
Because most domesticates show reduced genetic diversity relative to their wild counterparts, effort has been made to identify agronomically useful variation in crop wild relatives \citep{flint2009wide}. Often, after identification, the alleles conferring these beneficial traits are bred into domesticates for crop improvement. For example, \emph{Oryza rufipogon}, the wild progenitor of domesticated rice, has proven useful for the integration of a number of beneficial QTL controlling traits such as grain size and yield into domesticated rice \citep{KovachMcCouch2008}. In addition to researching the role of wild alleles in domesticates, researchers have also investigated the role of variation in domesticated taxa in the evolution of feral and weedy populations \citep{ellstrand2010crops}. A recent paper examining the genomic changes associated with rabbit domestication found that many domestication phenotypes are due to mutations in many small effect loci, and that many of these mutations are still found segregating in natural populations of wild rabbit, suggesting that selection acting on standing variation \citep{Rabbit}. There are numerous examples of weedy plants evolving to mimic their domestic counterpart, and even some instances where weedy plants have evolved domesticates (reviewed in \citealt{ellstrand2010crops}). But even though domesticated alleles are often found segregating in wild relatives \citep{Gallavotti2004, SigmonVollbrecht2010}, we know almost nothing about the ecological role of this variation in natural populations. In this paper we present an ecological genetic analysis of the domestication locus \emph{tb1} in natural populations of the wild ancestor of domesticated maize.

>>>>

Domesticated crops and their wild progenitors provide an excellent system in which to study adaptation and genomic changes associated with human-mediated selection \citep{Ross-Ibarra2007}. 
Plant domestication usually involves a suite of phenotypic changes such as loss of seed shattering and increased fruit or grain size, which are commonly referred to as `domestication syndrome' \citep{OlsenWendel2013}, and much of the study of domestication has focused on understanding the genetic variation underlying these traits \citep{OlsenGross2010}. 
Because most domesticates show reduced genetic diversity relative to their wild counterparts, effort has been made to identify agronomically useful variation in crop wild relatives \citep{flint2009wide}. Often, after identification, the alleles conferring these beneficial traits are bred into domesticates for crop improvement. For example, \emph{Oryza rufipogon}, the wild progenitor of domesticated rice, has proven useful for the integration of a number of beneficial QTL controlling traits such as grain size and yield into domesticated rice \citep{KovachMcCouch2008}. In addition to researching the role of wild alleles in domesticates, researchers have also investigated the role of variation in domesticated taxa in the evolution of feral and weedy populations \citep{ellstrand2010crops}. A recent paper examining the genomic changes associated with rabbit domestication found that many domestication phenotypes are due to mutations in many small effect loci, and that many of these mutations are still found segregating in natural populations of wild rabbit, suggesting that selection acted on standing variation \citep{Rabbit}. There are numerous examples of weedy plants evolving to mimic their domestic counterpart, and even some instances where weedy plants have evolved domesticates (reviewed in \citealt{ellstrand2010crops}). But even though domesticated alleles are often found segregating in wild relatives \citep{Gallavotti2004, SigmonVollbrecht2010}, we know almost nothing about the ecological role of this variation in natural populations. In this paper we present an ecological genetic analysis of the domestication locus \emph{tb1} in natural populations of the wild ancestor of domesticated maize.
